---
title: "p8105_hw5_xf2226"
author: "Xin Fang"
date: "11/20/2021"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis",
  digits = 3
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d 
knitr::opts_chunk$set(
  fig.height = 6,
  fig.width = 8,
  message = F,
  warning = F 
  )
```

# Problem 1 
The code chunk below imports and cleans the data
```{r}
homicides_df = 
  read_csv("./data/homicide-data.csv", na = c("", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved")
    ) %>% 
  relocate(city_state) %>% 
  filter(city_state != "TulsaAL")
```

Let's focus on Baltimore MD 

```{r}
baltimore_df = 
  homicides_df %>% 
  filter(city_state == "BaltimoreMD")

baltimore_summary = baltimore_df %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  )

baltimore_test = 
  prop.test(x = baltimore_summary %>% pull(unsolved), 
          n = baltimore_summary %>% pull(n))

baltimore_test %>% 
  broom::tidy()
```

Let's try to iterate across cities

First, write a function
```{r}
prop_test_function = function(city_df) {
  city_summary = 
    city_df %>% 
    summarize(
      unsolved = sum(resolution == "unsolved"),
      n = n()
    )
  
  city_test = 
    prop.test(x = city_summary %>% pull(unsolved), 
            n = city_summary %>% pull(n))
  
  return(city_test)
}

prop_test_function(baltimore_df)
```

Let's map the function
```{r}
results_df = 
  homicides_df %>% 
  nest(data = uid:resolution) %>% 
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))
```

Try to make a plot showing estimates and confidence intervals 

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

```{r}
homicides_df %>% 
  group_by(city_state) %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  ) %>% 
  mutate(
    test_results = map2(unsolved, n, prop.test), 
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))
```

# Problem 2 

Load the control and experimental data set
```{r}
research_data = tibble(
  files = list.files("./data/case-control/"),
  data = map(str_c("./data/case-control/",files), read_csv)
)
```

Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary
```{r}
research_cleaned = 
  research_data %>% 
  unnest(data) %>% 
  mutate(research_arm = ifelse(str_detect(files, "con"), "Control Arm", "Experimental Arm")) %>% 
  mutate(subject_id = (substr(files, 5, 6))) %>% 
  select(subject_id, research_arm, starts_with("week")) %>%
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "data"
  )
```

A spaghetti plot showing observations on each subject over time, and comment on differences between groups.
```{r}
research_cleaned %>% 
  ggplot(aes(x = week, y = data, group = subject_id, color = subject_id)) +
  geom_point() +
  geom_line() + 
  facet_grid(. ~ research_arm) +
  theme(legend.position = "bottom", plot.title = element_text(hjust = 0.5)) +
  labs(
    title = "Observation Data For Each Subject from Week 1 to Week 8",
    x = "Week",
    y = "Data",
    color = "Subject ID"
  )
```

From the above spaghetti plot we can see that, for subjects in the control arm, their observation data remained roughly unchanged (with a very slight overall decrease) over the 8-week study period. The majority of the collected data ranged from ~-1.75 to ~3.75. For subjects in the experimental arm, we see an overall increasing trend of observation data, which means, overall, subjects in the experimental arm are getting higher observation data from week 1 to week 8. The actual interpretation of this will depend on the study context. 


# Problem 3 
Importing the Data
```{r import data}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

Write a Function
```{r function}
fill_in_missing = function(x) {
  if (is.numeric(x)) {
    ifelse(is.na(x) == T, mean(x, na.rm = T), x)
  }
  else if (is.character(x))　{
    ifelse(is.na(x) == T, "virginica", x)
  }
  else if (!is.numeric(x) & !is.character(x)) {
     x == "Warning: Argument x neither numeric nor character"
  } 
}
```

Using the Function to fill in missing values in the iris data set
```{r}
iris_without_missing = map_df(iris_with_missing, fill_in_missing)
```